Rapid cycleway prioritisation tool

### 2020-06-01 code/index.Rmd
keeping groups

Please provide feedback on these preliminary results on this [web form (estimated time to complete: 5 minites)](https://urldefense.proofpoint.com/v2/url?u=https-3A__forms.office.com_Pages_ResponsePage.aspx-3Fid-3DqO3qvR3IzkWGPlIypTW3y9orQ9urif9IgBaXiRS9eEpUM0JCTDRFTTEwSDRVMUs0VVhVWEdGRDA3RS4u&d=DwMCaQ&c=troKkvwivNn_CddsvWCHHPiPoFoTgTGIbXJULvYU158&r=DXeEYtdSYDBZN2DBwEgAHMmX5PQ_ob9r2MynFWta2mU&m=mkyUa3RIC9d5LSrHUqk_WdstQR1OQuTWyYLBecHFMm0&s=dD7GVcQbjZ2AcdCObSe-rNKmLLDBhu98ChFupIIrlJA&e=).

@@

## 1. Key cycle routes

@@

## 3. Spare lane(s) (not shown be default)

@@

## 4. Width >= 10m

>>>>

Please provide feedback on these preliminary results on this [web form (estimated time to complete: 5 minutes)](https://urldefense.proofpoint.com/v2/url?u=https-3A__forms.office.com_Pages_ResponsePage.aspx-3Fid-3DqO3qvR3IzkWGPlIypTW3y9orQ9urif9IgBaXiRS9eEpUM0JCTDRFTTEwSDRVMUs0VVhVWEdGRDA3RS4u&d=DwMCaQ&c=troKkvwivNn_CddsvWCHHPiPoFoTgTGIbXJULvYU158&r=DXeEYtdSYDBZN2DBwEgAHMmX5PQ_ob9r2MynFWta2mU&m=mkyUa3RIC9d5LSrHUqk_WdstQR1OQuTWyYLBecHFMm0&s=dD7GVcQbjZ2AcdCObSe-rNKmLLDBhu98ChFupIIrlJA&e=).

@@

## 1. Cohesive network

@@

## 3. Spare lane(s) (not shown by default)

@@

## 4. Width >= 10m (not shown by default)
